Formal Synthesis of Digital Controllers for Observable Continuous Plants with Transient Performance Specifications

### 2018-01-27 TACAS2018/paper.tex
results intro

%-------------------------------
\subsection{Transient response} 
\label{sec:transientspecification}
%-------------------------------
In many cases the speed of the response \note{you mean the step response - this concept is undefined}, i.e. how fast it converges to the set point, is a requirement of great importance. 
This is given as a ``settling time.''

@@

%-------------------------------
\subsection{Results}
\label{exp:results}
%-------------------------------
\note{Start with a description of the results, e.g. ``We managed to synthesise controllers in X of the cases. Average time ... In the rest of the cases ...''}.

@@

@@

The median run-times for our benchmark sets are under a minute, and the
maximum observed synthesis time was under 10 minutes for a $4^{th}$ order system
($8^{th}$ order considering the observer).  We consider these times
short enough to be of practical use to control engineers.

There are cases for which the system fails to find a controller.  We use a
relatively short timeout, so it is possible longer timeouts would result in a
valid solution. However, as stated before, the solution is sound but incomplete,
so it is impossible to tell if a solution exists in these cases.

>>>>

%-------------------------------
\subsection{Transient response} 
\label{sec:transientspecification}
%-------------------------------
In many cases the response time of the system\note{you mean the step response - this concept is undefined}, i.e. how fast it converges to the set point, is a requirement of great importance. 
This is given as a ``settling time.''

@@

%-------------------------------
\subsection{Results}
\label{exp:results}
%-------------------------------

@@

Using the described technique we managed to synthesize controllers for X benchmarks, with a median synthesis time of $18.8$ seconds.
%and the maximum observed synthesis time was under 10 minutes for a $4^{th}$ order system ($8^{th}$ order considering the observer).
We consider these times short enough to be of practical use to control engineers.
There are cases for which the system fails to find a controller.  We use a
relatively short timeout, so it is possible longer timeouts would result in a
valid solution. However, as stated before, the solution is sound but incomplete,
so it is impossible to tell if a solution exists in these cases.

@@
